### 2021-12-10 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c01929f4d4dbf64bab7adfa991b25d8cdd8d0e1e 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c25f23fc0e4b5d860718769d5da56065cc637a6c 🚀

@@

In order to examine how these values change w.r.t. the skill and bias,
we performed a grid exploration of the values of \(s\) (from 0 to 1),
and of \(\text{logit}(b)\), and visualize the result for a connectance
of \textbf{TODO}.

\begin{figure}
\hypertarget{fig:analytics}{%
\centering
\includegraphics{figures/analytics.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). Accuracy increases with skill, but
also increases when the bias tends towards estimating \emph{fewer}
interactions. The \(F_1\) score increases with skill but also increases
when the bias tends towards estimating \emph{more} interactions; PPV
behaves in the same way. Interestingly, \(\kappa\) responds as expected
to skill (being negative whenever \(s < 0.5\)), and peaks for values of
\(b \approx 0.5\); nevertheless, the value of bias for which \(\kappa\)
is maximized in \emph{not} \(b=0.5\), but instead increases with
classifier skill. In other words, at equal skill, maximizing \(\kappa\)
would lead to select a \emph{more} bias
classifier.}\label{fig:analytics}
}
\end{figure}

>>>>

In all further simulations, the confusion matrix \(\mathbf{C}\) is
transformed so that it sums to 1.

@@

In order to examine how these values change w.r.t. the skill and bias,
we performed a grid exploration of the values of \(\text{logit}(s)\) and
\(\text{logit}(b)\) linearly from \(-10\) to \(10\), and visualize the
result for a connectance of \(\rho = 0.15\), which is within the range
of usually observed connectance values for empirical food webs.

\begin{figure}
\hypertarget{fig:analytics}{%
\centering
\includegraphics{figures/analytics.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). Accuracy increases with skill, but
also increases when the bias tends towards estimating \emph{fewer}
interactions. The \(F_1\) score increases with skill but also increases
when the bias tends towards estimating \emph{more} interactions; PPV
behaves in the same way. Interestingly, \(\kappa\) responds as expected
to skill (being negative whenever \(s < 0.5\)), and peaks for values of
\(b \approx 0.5\); nevertheless, the value of bias for which \(\kappa\)
is maximized in \emph{not} \(b=0.5\), but instead increases with
classifier skill. In other words, at equal skill, maximizing \(\kappa\)
would lead to select a \emph{more} biased
classifier.}\label{fig:analytics}
}
\end{figure}
